Spatial Reasoning and Data Displays

### 2015-01-09 Paper/Draft1/TestingVisualAptitude.Rnw
Citations for tests

Our experiment compares lineup performance with established tests, such as the visual search task (VST), paper folding test, card rotation test, and figure classification test. 
\comment{include citations for the tests}
The VST measures visual search speed, the paper folding and card rotation tests measures spatial manipulation ability, and the figure classification test measures inductive reasoning; 
all of these skills are at least peripherally recruited during the lineup task, but some may dominate in predicting performance on the lineup task. 
We hope to facilitate comparison of the lineup task to known cognitive tests, inform the design of future studies, and better understand human of the perception of statistical lineups. 
\comment {something went wrong with the last half sentence ... do you mean the human component in the statistical lineups?}

>>>>

Our experiment compares lineup performance with established tests, such as the visual search task (VST), paper folding test, card rotation test, and figure classification test. 
The VST measures visual search speed\cite{goldstein1973validity}, the paper folding and card rotation tests measures spatial manipulation ability, and the figure classification test measures inductive reasoning\cite{ekstrom1976manual}; 
all of these skills are at least peripherally recruited during the lineup task, but some may dominate in predicting performance on the lineup task. 
We hope to facilitate comparison of the lineup task to known cognitive tests, inform the design of future studies, and better understand human of the perception of statistical lineups. 
\comment {something went wrong with the last half sentence ... do you mean the human component in the statistical lineups?}
